### 2025-02-14 paper/sections/other/constraints.qmd
don't think this is worth it

# Data:
specs = [
    # ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    # ("(b)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    ("(c)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```

>>>>

# Data:
specs = [
    ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    ("(b)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    ("(c)", EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```
